Modeling Second-Language Learning from a Psychological Perspective

### 2018-03-27 doc/naaclhlt2018-latex/paper.tex
fixed a bug in description of language pairs

Educational software that aims to teach people new skills, languages, and
even academic subjects have become increasingly popular.  The wide-spread
deployment of these tools has created interesting opportunities to study
the process of learning in extremely large samples of learners in naturalistic
situations. The Duolingo shared task on Second Lanugage Acquisition Modeling (SLAM)
was a competitive modeling challenge run in early 2018~\cite{slam18}.
The challenge, organized by Duolingo\footnote{http://duolingo.com}, a popular second
language learning app, was
to use log data from thousand of users completing millions of exercises 
predict patterns of future translation mistakes in held-out data.  The data set was
divided into three sets covering students learning to translate English to Spanish (ES$\to$EN),
Spanish to English (ES$\to$EN), and French to English (FR$\to$EN).
This paper reports the approach used by our team which ended in third place 
for the ES$\to$EN data set, second place for the ES$\to$EN data set, and third place
for FR$\to$EN.

>>>>

Educational software that aims to teach people new skills, languages, and
academic subjects have become increasingly popular.  The wide-spread
deployment of these tools has created interesting opportunities to study
the process of learning in extremely large samples of learners in naturalistic
situations. The Duolingo shared task on Second Lanugage Acquisition Modeling (SLAM)
was a competitive modeling challenge run in early 2018~\cite{slam18}.
The challenge, organized by Duolingo\footnote{http://duolingo.com}, a popular second
language learning app, was
to use log data from thousand of users completing millions of exercises 
predict patterns of future translation mistakes in held-out data.  The data set was
divided into three sets covering Spanish speakers learning English ({\tt en\_es}),
English speakers learning Spanish ({\tt es\_en}), and English speakers learning
French ({\tt fr\_en}).
This paper reports the approach used by our team which ended in third place 
for the {\tt en\_es} data set, second place for {\tt es\_en}, and third place
for {\tt fr\_en}.
